Space-time plots

### 2017-06-13 Rmd/space-time.Rmd
Figure revisions, initial paragraph of discussion section.

# dat[st == 5, .N] / nrow(dat)

kwords <- cbind(c("field", "direct", "paleo", "remote", "automated", "other"),
                c("field", "field", "paleo", "remote", "automated", "other"))
cal[, study_type := tolower(study_type)]
# tst <- cal[, study_type]
for(i in 1:nrow(kwords)) {
  cal[like(study_type, kwords[i, 1]), study_type := kwords[i, 2]]
}
# cbind(tst, cal[, study_type])

# unique(dat$DOI)
# a <- unique(dato$DOI)
# b <- unique(dat$DOI)
# notin <- sort(a)[!sort(a) %in% sort(b)]
# dato[DOI %in% notin, 1:5, with = FALSE]
# dat[observer == "Ahmed" & journal == "Oecologia"]
# unique(cal$DOI) %in% unique(dat$DOI)
# match(cal$DOI, dat$DOI)
# match(dat$DOI, cal$DOI)
# dat[dat$DOI %in% cal$DOI, DOI]
# dat[cal$DOI %in% dat$DOI, ]
# cal[DOI == dat[cal$DOI %in% dat$DOI, DOI][11]]
# dat[DOI == dat[cal$DOI %in% dat$DOI, DOI][7]]
# dat[observer == "Treuer", unique(DOI)]  # 19

@@

## Data prep
### Merge full and calibration datasets
```{r, message=FALSE, warning=FALSE, results='hide'}
# dat2 <- copy(dat[, .(st, DOI, study_type, plot_res, n_sites, act_ext, eff_ext,
#                      samp_dur, t_btwn_samp, act_dur, eff_dur)])
# rnms <- c("st", "DOI", "study_type", "feature", "observer", "plot_res", 
#           "n_sites", "act_ext", "eff_ext", "samp_dur", "t_btwn_samp",
#           "act_dur", "eff_dur")
dat2 <- copy(dat[, .(DOI, study_type, plot_res, n_sites, act_ext, eff_ext,
                     samp_dur, t_btwn_samp, act_dur, eff_dur)])
# selind <- 3:ncol(dat2)
selind <- 4:ncol(dat2)
for(j in names(dat2)[selind]) set(dat2, j=j, value = as.numeric(dat2[[j]]))
rnms <- c("DOI", "study_type", "feature", "observer", "plot_res",
          "n_sites", "act_ext", "eff_ext", "samp_dur", "t_btwn_samp",
          "act_dur", "eff_dur")
calr <- cal[, rnms, with = FALSE]
selind <- c(3, 5:length(rnms))
for(j in names(calr)[selind]) set(calr, j=j, value = as.numeric(calr[[j]]))

@@

# extent
# hdatst <- hdatstat[[2]]$density
hdatst <- hdatstat_bt$ext$mu
l <- length(hdatst)
hds <- c("<1 ha", "<10 ha", "<100 ha", "<1000ha", "10-1K ha", ">10ha", "1K-1MK",
         ">1Kha", ">100Kha", ">1Mha")
inds <- list(1:6, 1:7, 1:8, 1:9, 8:9, 8:l, 10:12, 10:l, 12:l, 13:l)
sapply(1:length(inds), function(x) {
  v <- round(sum(hdatst[inds[[x]]]), 1)
  names(v) <- hds[x]
  v
})

@@

# choose which dataset to use
# kdat <- datf  # ordinary
kdat <- bootp_dt  # bootstrap
resdat3 <- data.table(x = log10(to_infin_byond(kdat$t_btwn_samp)), 
                      y = log10(kdat$plot_res))
resdat3 <- resdat3[round(x, 8) != 6.56229286]  # remove one-time observations
resdat3[, n := 1]  # set up count column
# resdat3$n <- rep(1, nrow(resdat3))
rx <- range(resdat3$x)
rx <- round(rx / 0.5) * 0.5  # round to nearest 0.5
rx[1] <- -5  # set min interval to less than second
#rx[2] <- 6.56
rx[2] <- 5.57  # set max interval to millenium
resdat3[x < rx[1], x := rx[1]]
resdat3[x > rx[2], x := rx[2]]
ry <- range(aaxis1$logres)
ry[1] <- -5  # set limits to 0.01 cm^2
resdat3[y < ry[1], y := ry[1]]
resdat3[y > ry[2], y := ry[2]]
coordinates(resdat3) <- ~x + y

# extent
extdat3 <- data.table(x = log10(kdat$eff_dur),#log10(kdat$act_dur), 
                      y = log10(kdat$eff_ext))#log10(kdat$act_ext))
extdat3 <- extdat3[!is.na(x) & !is.na(y)] # cut out null values
# extdat3$n <- rep(1, nrow(extdat3))
extdat3[, n := 1]  # set up count column
ex <- range(taxis2$logdays)
ex <- c(floor(ex[1]), 5.56) ### should this be 5.57?  #ceiling(ex[2]))
extdat3[x < ex[1], x := ex[1]]
extdat3[x > ex[2], x := ex[2]]
ey <- range(aaxis2$logarea)
extdat3[y < ey[1], y := ey[1]]
extdat3[y > ey[2], y := ey[2]]
coordinates(extdat3) <- ~x + y

# temporal framing
tempdat <- data.table(x = log10(to_infin_byond(kdat$t_btwn_samp)), 
                      y = log10(kdat$eff_dur))#kdat$act_dur))
# tt <- data.table(x = log10(kdat$t_btwn_samp), y = log10(kdat$eff_dur))
# range(tt$x - tempdat$x)
# tempdat[x != log10(365 * 10000)]
tempdat <- tempdat[!is.na(x) & !is.na(y)] # cut out null values
tempdat <- tempdat[round(x, 8) != 6.56229286, ]  # remove one-time observations

tempdat[x > y, .N] / tempdat[, .N]

# tempdat$n <- rep(1, nrow(tempdat))
tempdat[, n := 1]
tx <- range(tempdat$x)
tx <- round(rx / 0.5) * 0.5  # round to nearest 0.5
tx[2] <- 6.6  # just above 10 KA
# tx[2] <- 5.56
tempdat[x < rx[1], x := rx[1]]
tempdat[x > rx[2], x := rx[2]]
ty <- range(taxis2$logdays)
# ty <- c(floor(ty[1]), 5.56)#ceiling(ex[2]))
ty <- c(floor(ty[1]), 6.6)  # just above 10 KA
tempdat[y < ty[1], y := ty[1]]
tempdat[y > ty[2], y := ty[2]]
coordinates(tempdat) <- ~x + y

# spatial framing
spatdat <- data.table(x = log10(kdat$plot_res), y = log10(kdat$eff_ext))#act_ext))
spatdat <- spatdat[!is.na(x) & !is.na(y)] # cut out null values
# spatdat$n <- rep(1, nrow(spatdat))
spatdat[, n := 1]
sx <- range(aaxis1$logres)
sx[1] <- -5  # set limits to 0.01 cm^2
spatdat[x < sx[1], y := sx[1]]
spatdat[x > sx[2], y := sx[2]]
sy <- range(aaxis2$logarea)
spatdat[y < sy[1], y := sy[1]]
spatdat[y > sy[2], y := sy[2]]
coordinates(spatdat) <- ~x + y

# densities
# resolution
rres3 <- kdensity(rx[1], rx[2], ry[1], ry[2], 0.1, resdat3, 1)
rres3 <- (rres3 / cellStats(rres3, sum)) * 100

# extent
rext3 <- kdensity(ex[1], ex[2], ey[1], ey[2], 0.1, extdat3, 1)
rext3 <- (rext3 / cellStats(rext3, sum)) * 100

# temporal
tres <- kdensity(tx[1], tx[2], ty[1], ty[2], 0.1, tempdat, 1)
tres <- (tres / cellStats(tres, sum)) * 100
# spatial
sres <- kdensity(sx[1], sx[2], sy[1], sy[2], 0.1, spatdat, 1)
sres <- (sres / cellStats(sres, sum)) * 100

@@

# temporal
image(tres, axes = FALSE, xlab = "", ylab = "", col = cols)
for(i in 1:2) {  # using taxis2 values for both axes because same
  axis(i, at = taxis2$logdays[-5], labels = tlab2[-5], las = 2,
       cex.axis = cxa, tcl = -0.2)
}
# axis(1, at = taxis1$logdays[-c(5)], labels = tlab1[-c(5)], 
#      las = 2, tcl = -0.2, cex.axis = cxa)
mtext("Interval", 1, cex = cxa, line = ll)
mtext("Duration", 2, cex = cxa, line = ll)
# brks <- brkfun(tres, 0.02, 100)  # breaks
brks <- brkfun(tres, 0.01, cuts)  # breaks
aargs <- list(mgp = c(3, 0.25, 0), at = brks$labs, labels = brks$labs, 
              cex.axis = cxa, tcl = -0.1)
plot(tres, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
     legend.shrink = 0.9, col = cols)
mtext("D", side = 3, line = -1, cex = 0.8, adj = 0.05, col = "white")
dev.off()

# image(rres3, col = rev(terrain.colors(100)))
# image(rext3, col = rev(terrain.colors(100)))
# datf[, points(log10(eff_dur), log10(eff_ext), pch = 20, cex = 0.5)]
# datf[like(study_type, "remote"), {
#   points(log10(eff_dur), log10(eff_ext), pch = 20, cex = 0.5, col = "blue")
# }]
# points(resdat3$x, resdat3$y, pch = 20, cex = 0.5)
# image(sres, col = rev(terrain.colors(100)))
# datf[, points(log10(plot_res), log10(eff_ext), pch = 20, cex = 0.5)]
# datf[like(study_type, "remote"), {
#   points(log10(plot_res), log10(eff_ext), pch = 20, cex = 0.5, col = "blue")
#   abline(lm(log10(eff_ext) ~ log10(plot_res)))
# }]
# datf[like(study_type, "field"), {
#   points(log10(plot_res), log10(eff_ext), pch = 20, cex = 0.5, col = "red")
#   abline(lm(log10(eff_ext) ~ log10(plot_res)))
# }]
# points(spatdat$x, spatdat$y, pch = 20, cex = 0.5)

# bootp_dt[!t_btwn_samp == 365 * 10000, {
#   mean(t_btwn_samp[eff_dur > 30 & eff_dur < 365])
# }]
# bootp_dt[!t_btwn_samp == 365 * 10000, {
#   mean(t_btwn_samp[eff_dur > 365 & eff_dur <= (365 * 10)])
# }]

@@

### Figure 3
```{r, eval=FALSE}
# actual versus effective duration
kdat <- bootp_dt  # bootstrap
# tempdat2 <- data.table(x = log10(kdat$act_dur), y = log10(kdat$eff_dur))
tempdat2 <- data.table(x = log10(kdat$eff_dur), y = log10(kdat$act_dur))
dinds <- kdat[, which(t_btwn_samp == 365 * 10000)]  # drop unreplicated obs
tempdat2 <- tempdat2[-dinds, ]
tempdat2 <- tempdat2[!is.na(x) & !is.na(y)] # cut out null values
tempdat2[, n := 1]  # set up count column
tx <- range(taxis2$logdays)
tx <- c(floor(ex[1]), 5.56) ### should this be 5.57?  #ceiling(ex[2]))
tempdat2[x < tx[1], x := tx[1]]
tempdat2[x > tx[2], x := tx[2]]
ty <- range(taxis2$logdays)
ty <- c(floor(ex[1]), 5.56) ### should this be 5.57?  #ceiling(ex[2]))
tempdat2[y < tx[1], y := tx[1]]
tempdat2[y > tx[2], y := tx[2]]
coordinates(tempdat2) <- ~x + y

# extent
# extdat4 <- data.table(x = log10(kdat$act_ext), y = log10(kdat$eff_ext))
extdat4 <- data.table(x = log10(kdat$eff_ext), y = log10(kdat$act_ext))
extdat4 <- extdat4[!is.na(x) & !is.na(y)] # cut out null values
extdat4[, n := 1]  # set up count column
ex <- range(aaxis2$logarea)
extdat4[x < ex[1], x := ex[1]]
extdat4[x > ex[2], x := ex[2]]
ey <- range(aaxis2$logarea)
extdat4[y < ey[1], y := ey[1]]
extdat4[y > ey[2], y := ey[2]]
coordinates(extdat4) <- ~x + y

# densities
# temporal 
tres2 <- kdensity(tx[1], tx[2], ty[1], ty[2], 0.1, tempdat2, 1)
tres2 <- (tres2 / cellStats(tres2, sum)) * 100

# extent
rext4 <- kdensity(ex[1], ex[2], ey[1], ey[2], 0.1, extdat4, 1)
rext4 <- (rext4 / cellStats(rext4, sum)) * 100

# cxa = 0.7
ll <- 3.5
cxa = 0.7
stps <- sapply(c(3, 4), function(x) which(kdat$st == x))  # IDs rs/auto/paleo
pchs <- list(1, "+")
cexs <- c(0.4, 0.6)
cuts <- 40
bump <- 3
cols <- inferno(cuts + bump)[-c(2:(bump + 1))]
# plot(1:cuts, col = cols, pch = 20)

# par(mfrow = c(1, 2))
# datf[, {
#   # sel = which()
#   eext = log10(eff_ext)
#   aext = log10(act_ext)
#   edur = log10(eff_dur[t_btwn_samp != 365 * 10000])
#   adur = log10(act_dur[t_btwn_samp != 365 * 10000])
#   plot(aext, eext - aext)
#   plot(adur, edur - adur)
#   length(edur)
# }]

@@

# check number of drops due to eff < act
# hdat_bs2_ns <- do.call(rbind, lapply(hdat_bs2, function(x) x$Ns))
# summary(bootperturb[[1]][, .N] - hdat_bs2_ns[, 1])
# summary(bootperturb[[1]][t_btwn_samp != 365 * 10000, .N] - hdat_bs2_ns[, 2])

# extract regression coefficients
# hdat_bs2_elm <- do.call(rbind, lapply(hdat_bs2, function(x) coef(x$elm)[, 1]))
# hdat_bs2_tlm <- do.call(rbind, lapply(hdat_bs2, function(x) coef(x$tlm)[, 1]))

@@

# Kernel density version
pdf("paper/figures/act_v_eff.pdf", width = 7, height = 3)
par(mfrow = c(1, 2), mar = c(4.5, 4.5, 0.3, 3), oma = c(0, 0, 0.2, 1), 
    mgp = c(2, 0.25, 0))

mtl <- 3
# spatial extents
image(rext4, axes = FALSE, xlab = "", ylab = "", col = cols)
axis(1, at = aaxis2$logarea, labels = alab2, las = 2,
     cex.axis = cxa, tcl = -0.2)
axis(2, at = aaxis2$logarea, labels = alab2, las = 2, cex.axis = cxa,
     tcl = -0.2)
brks <- brkfun(rext4, 0.01, cuts)  # breaks
aargs <- list(mgp = c(3, 0.25, 0), at = brks$labs, labels = brks$labs, 
              cex.axis = cxa, tcl = -0.1)
mtext("Actual extent", 2, cex = cxa, line = mtl)
mtext("Effective extent", 1, cex = cxa, line = mtl)
plot(rext4, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
     legend.shrink = 0.9, col = cols)
mtext("A", side = 3, line = -1, cex = 0.8, adj = 0.05, col = "white")

# temporal extents
image(tres2, axes = FALSE, xlab = "", ylab = "", col = cols)
axis(1, at = taxis1$logdays[-c(5)], labels = tlab1[-c(5)], 
     las = 2, tcl = -0.2, cex.axis = cxa)
axis(2, at = taxis1$logdays[-c(5)], labels = tlab1[-c(5)], las = 2, tcl = -0.2, 
     cex.axis = cxa)
mtext("Actual duration", 2, cex = cxa, line = mtl)
mtext("Effective duration", 1, cex = cxa, line = mtl)
brks <- brkfun(tres2, 0.01, cuts)  # breaks
aargs <- list(mgp = c(3, 0.25, 0), at = brks$labs, labels = brks$labs, 
              cex.axis = cxa, tcl = -0.1)
plot(tres2, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
     legend.shrink = 0.9, col = cols)
     #col = rev(terrain.colors(cuts)))
mtext("B", side = 3, line = -1, cex = 0.8, adj = 0.05, col = "white")
dev.off()

@@

  image(x$ext, col = cols, axes = FALSE, xlab = "", ylab = "")
  if(i == 3) {
    axis(1, at = taxis2$logdays[-5], labels = tlab2[-5], las = 2,
         cex.axis = cxa, tcl = -0.2)
  }
  axis(2, at = aaxis2$logarea, labels = alab2, las = 2, cex.axis = cxa,
       tcl = -0.2)
  aargs <- list(mgp = c(3, 0.25, 0), #at = brklabs2, labels = brklabs2, 
                cex.axis = cxa, tcl = -0.1)
  plot(x$ext, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
       legend.shrink = 0.9, col = cols)#breaks = brks2, 
}
# # par(xpd = NA)
# for(j in c("in", "dev", "ndc", "nfc", "npc", "nic")) {
#   xx <- grconvertX(0.5, from = "user", to = j)
#   ii <- c(0.4, 0.6, 0.8, 1)
#   yy <- c(0.95, 0.75, 0.5, 0.25)
#   # yy <- c(-1, -5, -10, -20)
#   for(i in 1:length(ii)) {
#     y <- grconvertY(yy[i], from = "user", to = j)
#     text(x = xx, y = y, labels = paste("kernel =", ii[i]))
#     # par(xpd = NA)
#     # mtext(text = paste("kernel =", ii[i]), side = 3, line = yy[i])
#   }
# }
dev.off()

# plot(rrs, xlim = c(-5, 15), ylim = c(-5, 15), 
#      xlab = "Sample interval - log10(days)", 
#      ylab = "Plot resolution - log10(m^2)")
# plot(ers, box = FALSE, xlim = c(-5, 15), ylim = c(-5, 15), 
#      xlab = "Study duration - log10(days)", ylab = "Sampled area - log10(ha)")
# dev.off()

>>>>

kwords <- cbind(c("field", "direct", "paleo", "remote", "automated", "other"),
                c("field", "field", "paleo", "remote", "automated", "other"))
cal[, study_type := tolower(study_type)]
# tst <- cal[, study_type]
for(i in 1:nrow(kwords)) {
  cal[like(study_type, kwords[i, 1]), study_type := kwords[i, 2]]
}

@@

## Data prep
### Merge full and calibration datasets
```{r, message=FALSE, warning=FALSE, results='hide'}
dat2 <- copy(dat[, .(DOI, study_type, plot_res, n_sites, act_ext, eff_ext,
                     samp_dur, t_btwn_samp, act_dur, eff_dur)])
# selind <- 3:ncol(dat2)
selind <- 4:ncol(dat2)
for(j in names(dat2)[selind]) set(dat2, j=j, value = as.numeric(dat2[[j]]))
rnms <- c("DOI", "study_type", "feature", "observer", "plot_res",
          "n_sites", "act_ext", "eff_ext", "samp_dur", "t_btwn_samp",
          "act_dur", "eff_dur")
calr <- cal[, rnms, with = FALSE]
selind <- c(3, 5:length(rnms))
for(j in names(calr)[selind]) set(calr, j=j, value = as.numeric(calr[[j]]))

@@

# extent
# hdatst <- hdatstat[[2]]$density
hdatst <- hdatstat_bt$ext$mu
l <- length(hdatst)
hds <- c("<1 ha", "<10 ha", "<100 ha", "<1000ha", "<10Kha", "10-1k ha", "1k-10k",  
         "10k-100k", "100k-1Mk", ">1Kha", ">100Kha", ">1Mha")
inds <- list(1:6, 1:7, 1:8, 1:9, 1:10, 8:9, 10, 11, 12, 10:l, 12:l, 13:l)
sapply(1:length(inds), function(x) {
  v <- round(sum(hdatst[inds[[x]]]), 1)
  names(v) <- hds[x]
  v
})

@@

# choose which dataset to use
# kdat <- datf  # ordinary
kdat <- bootp_dt  # bootstrap
resdat3 <- data.table(x = log10(to_infin_byond(kdat$t_btwn_samp)), 
                      y = log10(kdat$plot_res))
resdat3 <- resdat3[round(x, 8) != 6.56229286]  # remove one-time observations
resdat3[, n := 1]  # set up count column
# resdat3$n <- rep(1, nrow(resdat3))
ilim <- range(resdat3$x)
ilim <- round(ilim / 0.5) * 0.5  # round to nearest 0.5
ilim[1] <- -5  # set min interval to less than second
#rx[2] <- 6.56
ilim[2] <- 5.57  # set max interval to millenium
resdat3[x < ilim[1], x := ilim[1]]
resdat3[x > ilim[2], x := ilim[2]]
rlim <- range(aaxis1$logres)
rlim[1] <- -5  # set limits to 0.01 cm^2
resdat3[y < rlim[1], y := rlim[1]]
resdat3[y > rlim[2], y := rlim[2]]
coordinates(resdat3) <- ~x + y

# extent
extdat3 <- data.table(x = log10(kdat$eff_dur),#log10(kdat$act_dur), 
                      y = log10(kdat$eff_ext))#log10(kdat$act_ext))
extdat3 <- extdat3[!is.na(x) & !is.na(y)] # cut out null values
# extdat3$n <- rep(1, nrow(extdat3))
extdat3[, n := 1]  # set up count column
dlim <- range(taxis2$logdays)
dlim <- c(floor(dlim[1]), 5.56) ### should this be 5.57?  #ceiling(ex[2]))
extdat3[x < dlim[1], x := dlim[1]]
extdat3[x > dlim[2], x := dlim[2]]
elim <- range(aaxis2$logarea)
extdat3[y < elim[1], y := elim[1]]
extdat3[y > elim[2], y := elim[2]]
coordinates(extdat3) <- ~x + y

# temporal framing (interval-duration)
tempdat <- data.table(x = log10(to_infin_byond(kdat$t_btwn_samp)), 
                      y = log10(kdat$eff_dur))#kdat$act_dur))
tempdat <- tempdat[!is.na(x) & !is.na(y)] # cut out null values
tempdat <- tempdat[round(x, 8) != 6.56229286, ]  # remove one-time observations

# tempdat$n <- rep(1, nrow(tempdat))
tempdat[, n := 1]
# tx <- range(tempdat$x)
# tx <- round(rx / 0.5) * 0.5  # round to nearest 0.5
tempdat[x < ilim[1], x := ilim[1]]
tempdat[x > ilim[2], x := ilim[2]]
dlimty <- range(taxis2$logdays)
# ty <- c(floor(ty[1]), 5.56)#ceiling(ex[2]))
# ty <- c(floor(ty[1]), 6.6)  # just above 10 KA
tempdat[y < elim[1], y := elim[1]]
tempdat[y > elim[2], y := elim[2]]
coordinates(tempdat) <- ~x + y

# spatial framing (res-extent)
spatdat <- data.table(x = log10(kdat$plot_res), y = log10(kdat$eff_ext))#act_ext))
spatdat <- spatdat[!is.na(x) & !is.na(y)] # cut out null values
# spatdat$n <- rep(1, nrow(spatdat))
spatdat[, n := 1]
# sx <- range(aaxis1$logres)
sx[1] <- -5  # set limits to 0.01 cm^2
spatdat[x < rlim[1], y := rlim[1]]
spatdat[x > rlim[2], y := rlim[2]]
# sy <- range(aaxis2$logarea)
spatdat[y < elim[1], y := elim[1]]
spatdat[y > elim[2], y := elim[2]]
coordinates(spatdat) <- ~x + y

# # interval-extent
# iextdat <- data.table(x = log10(kdat$t_btwn_samp), y = log10(kdat$eff_ext))
# iextdat <- iextdat[!is.na(x) & !is.na(y)] # cut out null values
# iextdat <- iextdat[round(x, 8) != 6.56229286, ]  # remove one-time observations
# iextdat[, n := 1]
# iextdat[x < ilim[1], x := ilim[1]]
# iextdat[x > ilim[2], x := ilim[2]]
# iextdat[y < elim[1], y := elim[1]]
# iextdat[y > elim[2], y := elim[2]]
# coordinates(iextdat) <- ~x + y
# 
# # resolution-duration
# rdurdat <- data.table(x = log10(kdat$eff_dur), y = log10(kdat$plot_res))
# rdurdat <- rdurdat[!is.na(x) & !is.na(y)] # cut out null values
# rdurdat[, n := 1]
# rdurdat[x < dlim[1], x := dlim[1]]
# rdurdat[x > dlim[2], x := dlim[2]]
# rdurdat[y < rlim[1], y := rlim[1]]
# rdurdat[y > rlim[2], y := rlim[2]]
# coordinates(rdurdat) <- ~x + y

# densities
# interval-resolution
rres3 <- kdensity(ilim[1], ilim[2], rlim[1], rlim[2], 0.1, resdat3, 1)
rres3 <- (rres3 / cellStats(rres3, sum)) * 100

# duration-extent
rext3 <- kdensity(dlim[1], dlim[2], elim[1], elim[2], 0.1, extdat3, 1)
rext3 <- (rext3 / cellStats(rext3, sum)) * 100

# interval-duration
tres <- kdensity(ilim[1], ilim[2], dlim[1], dlim[2], 0.1, tempdat, 1)
tres <- (tres / cellStats(tres, sum)) * 100

# resolution-extent
sres <- kdensity(rlim[1], rlim[2], elim[1], elim[2], 0.1, spatdat, 1)
sres <- (sres / cellStats(sres, sum)) * 100

# # interval-extent
# iext <- kdensity(ilim[1], ilim[2], elim[1], elim[2], 0.1, iextdat, 1)
# iext <- (iext / cellStats(iext, sum)) * 100
# 
# # resolution-duration
# rdur <- kdensity(dlim[1], dlim[2], rlim[1], rlim[2], 0.1, rdurdat, 1)
# rdur <- (rdur / cellStats(rdur, sum)) * 100

@@

# temporal
image(tres, axes = FALSE, xlab = "", ylab = "", col = cols)
for(i in 1:2) {  # using taxis2 values for both axes because same
  axis(i, at = taxis2$logdays[-5], labels = tlab2[-5], las = 2,
       cex.axis = cxa, tcl = -0.2)
}
mtext("Interval", 1, cex = cxa, line = ll)
mtext("Duration", 2, cex = cxa, line = ll)
# brks <- brkfun(tres, 0.02, 100)  # breaks
brks <- brkfun(tres, 0.01, cuts)  # breaks
aargs <- list(mgp = c(3, 0.25, 0), at = brks$labs, labels = brks$labs, 
              cex.axis = cxa, tcl = -0.1)
plot(tres, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
     legend.shrink = 0.9, col = cols)
mtext("D", side = 3, line = -1, cex = 0.8, adj = 0.05, col = "white")
dev.off()

# image(rdur, axes = FALSE, xlab = "", ylab = "", col = cols)
# plot(rdur, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
#      legend.shrink = 0.9, col = cols)

@@

### Figure 3
```{r, eval=FALSE}
# actual versus effective duration
# kdat <- bootp_dt  # bootstrap
# # tempdat2 <- data.table(x = log10(kdat$act_dur), y = log10(kdat$eff_dur))
# tempdat2 <- data.table(x = log10(kdat$eff_dur), y = log10(kdat$act_dur))
# dinds <- kdat[, which(t_btwn_samp == 365 * 10000)]  # drop unreplicated obs
# tempdat2 <- tempdat2[-dinds, ]
# tempdat2 <- tempdat2[!is.na(x) & !is.na(y)] # cut out null values
# tempdat2[, n := 1]  # set up count column
# tx <- range(taxis2$logdays)
# tx <- c(floor(ex[1]), 5.56) ### should this be 5.57?  #ceiling(ex[2]))
# tempdat2[x < tx[1], x := tx[1]]
# tempdat2[x > tx[2], x := tx[2]]
# ty <- range(taxis2$logdays)
# ty <- c(floor(ex[1]), 5.56) ### should this be 5.57?  #ceiling(ex[2]))
# tempdat2[y < tx[1], y := tx[1]]
# tempdat2[y > tx[2], y := tx[2]]
# coordinates(tempdat2) <- ~x + y
# 
# # extent
# # extdat4 <- data.table(x = log10(kdat$act_ext), y = log10(kdat$eff_ext))
# extdat4 <- data.table(x = log10(kdat$eff_ext), y = log10(kdat$act_ext))
# extdat4 <- extdat4[!is.na(x) & !is.na(y)] # cut out null values
# extdat4[, n := 1]  # set up count column
# ex <- range(aaxis2$logarea)
# extdat4[x < ex[1], x := ex[1]]
# extdat4[x > ex[2], x := ex[2]]
# ey <- range(aaxis2$logarea)
# extdat4[y < ey[1], y := ey[1]]
# extdat4[y > ey[2], y := ey[2]]
# coordinates(extdat4) <- ~x + y
# 
# # densities
# # temporal 
# tres2 <- kdensity(tx[1], tx[2], ty[1], ty[2], 0.1, tempdat2, 1)
# tres2 <- (tres2 / cellStats(tres2, sum)) * 100
# 
# # extent
# rext4 <- kdensity(ex[1], ex[2], ey[1], ey[2], 0.1, extdat4, 1)
# rext4 <- (rext4 / cellStats(rext4, sum)) * 100
# 
# # cxa = 0.7

# plot params
ex <- range(aaxis2$logarea)
ey <- range(aaxis2$logarea)
ll <- 3.5
cxa = 0.7
stps <- sapply(c(3, 4), function(x) which(kdat$st == x))  # IDs rs/auto/paleo
pchs <- list(1, "+")
cexs <- c(0.4, 0.6)
cuts <- 40
bump <- 3
cols <- inferno(cuts + bump)[-c(2:(bump + 1))]
# # plot(1:cuts, col = cols, pch = 20)
# 
# # par(mfrow = c(1, 2))
# # datf[, {
# #   # sel = which()
# #   eext = log10(eff_ext)
# #   aext = log10(act_ext)
# #   edur = log10(eff_dur[t_btwn_samp != 365 * 10000])
# #   adur = log10(act_dur[t_btwn_samp != 365 * 10000])
# #   plot(aext, eext - aext)
# #   plot(adur, edur - adur)
# #   length(edur)
# # }]

@@

@@

# # Kernel density version
# pdf("paper/figures/act_v_eff.pdf", width = 7, height = 3)
# par(mfrow = c(1, 2), mar = c(4.5, 4.5, 0.3, 3), oma = c(0, 0, 0.2, 1), 
#     mgp = c(2, 0.25, 0))
# 
# mtl <- 3
# # spatial extents
# image(rext4, axes = FALSE, xlab = "", ylab = "", col = cols)
# axis(1, at = aaxis2$logarea, labels = alab2, las = 2,
#      cex.axis = cxa, tcl = -0.2)
# axis(2, at = aaxis2$logarea, labels = alab2, las = 2, cex.axis = cxa,
#      tcl = -0.2)
# brks <- brkfun(rext4, 0.01, cuts)  # breaks
# aargs <- list(mgp = c(3, 0.25, 0), at = brks$labs, labels = brks$labs, 
#               cex.axis = cxa, tcl = -0.1)
# mtext("Actual extent", 2, cex = cxa, line = mtl)
# mtext("Effective extent", 1, cex = cxa, line = mtl)
# plot(rext4, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
#      legend.shrink = 0.9, col = cols)
# mtext("A", side = 3, line = -1, cex = 0.8, adj = 0.05, col = "white")
# 
# # temporal extents
# image(tres2, axes = FALSE, xlab = "", ylab = "", col = cols)
# axis(1, at = taxis1$logdays[-c(5)], labels = tlab1[-c(5)], 
#      las = 2, tcl = -0.2, cex.axis = cxa)
# axis(2, at = taxis1$logdays[-c(5)], labels = tlab1[-c(5)], las = 2, tcl = -0.2, 
#      cex.axis = cxa)
# mtext("Actual duration", 2, cex = cxa, line = mtl)
# mtext("Effective duration", 1, cex = cxa, line = mtl)
# brks <- brkfun(tres2, 0.01, cuts)  # breaks
# aargs <- list(mgp = c(3, 0.25, 0), at = brks$labs, labels = brks$labs, 
#               cex.axis = cxa, tcl = -0.1)
# plot(tres2, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
#      legend.shrink = 0.9, col = cols)
#      #col = rev(terrain.colors(cuts)))
# mtext("B", side = 3, line = -1, cex = 0.8, adj = 0.05, col = "white")
# dev.off()
```

@@

  image(x$ext, col = cols, axes = FALSE, xlab = "", ylab = "")
  if(i == 3) {
    axis(1, at = taxis2$logdays[-5], labels = tlab2[-5], las = 2,
         cex.axis = cxa, tcl = -0.2)
  }
  axis(2, at = aaxis2$logarea, labels = alab2, las = 2, cex.axis = cxa,
       tcl = -0.2)
  aargs <- list(mgp = c(3, 0.25, 0), #at = brklabs2, labels = brklabs2, 
                cex.axis = cxa, tcl = -0.1)
  plot(x$ext, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
       legend.shrink = 0.9, col = cols)#breaks = brks2, 
}
dev.off()
